New lower bounds for Schur and weak Schur numbers

### 2021-04-15 article/weakschur.tex
correction mode math

Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\pi_{a,b}\) the projection:
\[ \pi_{a,b}:x \longmapsto (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a}))\]
\end{definition}

We will note  the projection \(\pi\) and not \(\pi_{a,b}\) when there is no doubt about the a and b we use.

@@

\begin{proposition}
Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\), then we have: \(\pi(x+y)=x+\pi(y)\)
\end{proposition}

\textsc{Proof :}Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)

@@

\begin{align*}
 \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
& =x+ \pi(y)
\end{align*}

if \(x+\pi(y\geqslant a\):
\begin{align*}
 \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
& = x+\pi(y) - a +a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
& = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
& = x+\pi(y)
\end{align*}

\begin{proposition}
Let (x,y)\(\in (\mathbb{N}^*)^2\), \(\pi(\pi(x)+\pi(y))=\pi(x+y)\)
\end{proposition}

\textsc{Proof :}Let (x,y)\(\in (\mathbb{N}^*)^2\),

\begin{align*}
 \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y)\text{ mod a})\\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})((Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a})+(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{y mod a})\text{ mod a}) \\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ ((x mod a) + (y mod a)) mod a})\\
& =(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ x+y mod a})\\
& =\pi(x+y)
\end{align*}

@@

Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\lambda_{a,b}\) the projection:
\[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
\end{definition}

We will note  the projection \(\lambda\) and not \(\lambda_{a,b}\) when there is no doubt about the a and b we use.

@@

\begin{proposition}
Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\), \(x=a\lambda(x)+\pi(x)-a\)
\end{proposition}
\textsc{Proof :}Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\),
\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(\text{x mod a})+\mathbf{1}_{ [\![0,b]\!]}(\text{x mod a})\)

if x mod a \(>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+\text{x mod a}=x\)

if x mod a \(\leqslant b\):
\(a\lambda(x)+\pi(x)-a=a(\left\lfloor\dfrac{x}{a}\right\rfloor-1)+\text{x mod a}+a=x\)

@@

\begin{definition}
Let \( n \in \mathbb{N}^*\), we define \(\WS^+(n)\)=\(\max_{b\in \mathbb{N}^*} \{\WS_b^+(n)\}\)
\end{definition}

@@

\begin{theorem}
Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \(k\)
sum-free subsets of \([\![1,p]\!]\) and a partition of n subsets \((A_1,....,A_n)\) of \([\![1, q]\!]\) which is a
\(b\)-WSF of \(n\) colors and lenght \(q\),
 then there exists a partition of \([\![1, b+p \times (q-b)]\!]\) into \((k+n-1)\) weakly sum-free subsets.
\end{theorem}

@@

\begin{proposition}
Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a b-WSF-template of length \(p\) with \(k\) colors. Let
\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a colouring \(g\) of
\([\![b + 1, b + c]\!]\) with \(k\) colors such that:
\begin{itemize}
	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c)
	\implies g(\pi(x + y)) \neq f(x)\)
	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c)
\implies g(\pi(x + y)) \neq f(x)\)
\end{itemize}
Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
\end{proposition}

\textsc{Proof:} Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
We denote by \(g\) the colouring associated to the partition of \([\![1,q]\!]\) and \(h\) the
one associated to the partition of \([\![1,p]\!]\).
\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a b-WSF-template.}
\]
\[h : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } h(x) = h(y)
\Longrightarrow h(x+y) \neq h(x)
\]

Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such that:
\\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
\\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
\\\\
f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)

@@

We have to verify that f induces weakly-sum-free templates:\\
\\
\underline{if (x,y) \(\in (\mathcal{T})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\x+y\(<\)a+b since b\(<\)a and g(x)=f(x)=f(y)=g(y).
\\Hence f(x+y)=g(x+y)\(\neq\)g(x)=f(x)
\\\\
\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{C}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
We distinguish two cases:

\begin{itemize}
\item If x+\(\pi(y)\leqslant a+b\)
\\g(x)=f(x)=f(y)=g(\(\pi(y)\). Hence g(x)\(\neq g(x+\pi(y))=g(\pi(x+y))\) (qv previous proposition)
\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
\\else, \(f(x+y)=g(\pi(x+y))\neq g(x)=f(x)\)
\item If x+\(\pi(y)> a+b\), x+y\(>\)a+b and by definition of g, \(g(\pi(x+y))\neq g(x)\)
\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
\end{itemize}

\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{R}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Then, f(x)=f(y)=n. We distinguish two cases:

\begin{itemize}
\item If \(\lambda(y)=\lambda(x+y)\),
\\\(g(x)=g(\pi(y))=n \text{ since } g(y)=g(\pi(y))\)
\\Therefore \(g(\pi(x+y))=g(x+\pi(y)) \neq g(x)=n\)(qv previous proposition)
\\Hence \(f(x+y)=g(\pi(x+y))\neq n\)
\item If  \(\lambda(y)\neq \lambda(x+y)\), \(\lambda(y)+1= \lambda(x+y)\)\\
n=f(y)=n-1+h(\(\lambda(y)\)). Hence h(\(\lambda(y)\))=1.
\\Moreover h(1)=1, therefore \(h(\lambda(y)+1) \neq 1\)
\\if \(\pi(x+y) \in A_n\), \(f(x+y)=n-1+h(\lambda(x+y))>n\)
\end{itemize}

\underline{if (x,y) \(\in (\mathcal{C})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases:

\begin{itemize}
\item If \(\pi(x)+\pi(y)>q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) (qv previous proposition)
\\Hence \(g(\pi(x+y))= g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))\)
\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
\item If  \(\pi(x)+\pi(y)\leqslant q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) since g is sum-free for x\(>b\)
\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
\\else, \(f(x+y)=g(\pi(x+y))=g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))=f(x)\)

@@

\underline{if (x,y) \(\in \mathcal{C} \times \mathcal{R} \), \(f(x)\neq f(y)\)}\\

\underline{if (x,y) \(\in (\mathcal{R})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Let r(x)=\(\pi(x)-a\) and r(y)=\(\pi(y)-a\),
\\We proved that \(x=a\lambda(x)+\pi(x)-a\), therefore \(x=a\lambda(x)+\pi(x)\)
\\\(x+y=a(\lambda(x)+\lambda(y))+r(x)+r(y)\). We distinguish three cases:

@@

\item If \(r(x)+r(y)>b\), \(\pi(x)+\pi(y)>2a+b\)
\\Since g is a b-WSF template, \(g(\pi(\pi(x)+\pi(y))) \neq n\)
\\Therefore, \(g(\pi(x+y)) \neq n\) ie \(x+y \in \mathcal{C}\)
\\Hence \(f(x+y) <n\leqslant f(x)\)
\item If \(r(x)+r(y) \leqslant b - a\), \(\pi(x)+\pi(y)\leqslant b+a\)
\\Since g is sum-free for x\(>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
\\Hence, \(f(x+y) <n\leqslant f(x)\)
\end{itemize}

>>>>

Let \((a,b) \in (\mathbb{N}^*)^2\),\(a>b\), \(n \in \mathbb{N}^*\), we will define \(\pi_{a,b}\) the projection:
\[ \pi_{a,b}:x \longmapsto (Id+a\mathbf{1}_{ [\![0,b]\!]})(x \mod a))\]
\end{definition}

We will note  the projection \(\pi\) and not \(\pi_{a,b}\) when there is no doubt about the \(a\) and \(b\) we use.

@@

\begin{proposition}
Let x \(\in [\![1,b]\!]\), let  \(y \in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\), then we have: \(\pi(x+y)=x+\pi(y)\)
\end{proposition}

\textsc{Proof :}Let  \(x\in [\![1,b]\!]\), let  \(y\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)

@@

\begin{align*}
 \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+y \mod a)\\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a)\text{ since } \pi(y)\=y \mod a \\
& =x+ \pi(y)
\end{align*}

if \(x+\pi(y)\geqslant a\):
\begin{align*}
 \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+y \mod a)\\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a)\text{ since } \pi(y)=y \mod a \\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
& = x+\pi(y) - a +a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
& = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
& = x+\pi(y)
\end{align*}

\begin{proposition}
Let \((x,y)\in (\mathbb{N}^*)^2\), \(\pi(\pi(x)+\pi(y))=\pi(x+y)\)
\end{proposition}

\textsc{Proof :}Let \((x,y)\in (\mathbb{N}^*)^2\),

\begin{align*}
 \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y)\text{ mod a})\\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})((Id+a\mathbf{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathbf{1}_{ [\![0,b]\!]})(y \mod a)\ mod a) \\
& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
& =(Id+a\mathbf{1}_{ [\![0,b]\!]})( x+y \mod a)\\
& =\pi(x+y)
\end{align*}

@@

Let \((a,b) \in (\mathbb{N}^*)^2\), \(a>b\), let \(n \in\mathbb{N}\) we will define \(\lambda_{a,b}\) the projection:
\[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
\end{definition}

We will note  the projection \(\lambda\) and not \(\lambda_{a,b}\) when there is no doubt about the \(a\) and \(b\) we use.

@@

\begin{proposition}
Let \((a,b)\in (\mathbb{N}^*)^2\), \(a>b\), let  \(x\in \mathbb{N}^*\), \(x=a\lambda(x)+\pi(x)-a\)
\end{proposition}
\textsc{Proof :}Let \((a,b)\in (\mathbb{N}^*)^2\), \(a>b\), let  \(x\in \mathbb{N}^*\),
\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(\text{x mod a})+\mathbf{1}_{ [\![0,b]\!]}(x \mod a)\)

if \(x \mod a>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\)

if \(x \mod a \leqslant b\):
\(a\lambda(x)+\pi(x)-a=a(\left\lfloor\dfrac{x}{a}\right\rfloor-1)+\text{x mod a}+a=x\)

@@

\begin{definition}
Let \( n \in \mathbb{N}^*\), we define \(\WS^+(n)=\max_{b\in \mathbb{N}^*} \{\WS_b^+(n)\}\)
\end{definition}

@@

\begin{theorem}
Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \(k\)
sum-free subsets of \([\![1,p]\!]\) and a partition of \(n\) subsets \((A_1,....,A_n)\) of \([\![1, q]\!]\) which is a
\(b\)-WSF of \(n\) colors and lenght \(q\),
 then there exists a partition of \([\![1, b+p \times (q-b)]\!]\) into \((k+n-1)\) weakly sum-free subsets.
\end{theorem}

@@

\begin{proposition}
Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a \(b\)-WSF-template of length \(p\) with \(k\) colors. Let
\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a colouring \(g\) of
\([\![b + 1, b + c]\!]\) with \(k\) colors such that:
\begin{itemize}
	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c)
	\implies g(\pi(x + y)) \neq f(x)\)
	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c)
\implies g(\pi(x + y)) \neq f(x)\)
\end{itemize}
Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
\end{proposition}

\textsc{Proof:} Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let \(a=q-b\). \\
We denote by \(g\) the colouring associated to the partition of \([\![1,q]\!]\) and \(h\) the
one associated to the partition of \([\![1,p]\!]\).
\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a \(b\)-WSF-template.}
\]
\[h : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } h(x) = h(y)
\Longrightarrow h(x+y) \neq h(x)
\]

Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such that:
\\\\-if  \(x\leqslant b \text{ (we will note }x \in \mathcal{T}): f(x)=g(x)\)
\\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
\\\\
\(f\) is well defined because \(\pi\) is defined for \(x>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because \(h(\lambda(x))\leqslant k\)

@@

We have to verify that f induces weakly-sum-free templates:\\
\\
\underline{if (x,y) \(\in (\mathcal{T})^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\\(x+y<a+b\) since \(b<a\) and \(g(x)=f(x)=f(y)=g(y)\).
\\Hence \(f(x+y)=g(x+y)\neq g(x)=f(x)\)
\\\\
\underline{if \((x,y) \in \mathcal{T} \times \mathcal{C}\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
We distinguish two cases:

\begin{itemize}
\item If \(x+\pi(y)\leqslant a+b\)
\\\(g(x)=f(x)=f(y)=g(\pi(y)\). Hence \(g(x)\neq g(x+\pi(y))=g(\pi(x+y))\) (qv previous proposition)
\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
\\else, \(f(x+y)=g(\pi(x+y))\neq g(x)=f(x)\)
\item If \(x+\pi(y)> a+b\), \(x+y>a+b\) and by definition of \(g\), \(g(\pi(x+y))\neq g(x)\)
\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
\end{itemize}

\underline{if \((x,y) \in \mathcal{T} \times \mathcal{R}\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Then, \(f(x)=f(y)=n\). We distinguish two cases:

\begin{itemize}
\item If \(\lambda(y)=\lambda(x+y)\),
\\\(g(x)=g(\pi(y))=n \text{ since } g(y)=g(\pi(y))\)
\\Therefore \(g(\pi(x+y))=g(x+\pi(y)) \neq g(x)=n\)(qv previous proposition)
\\Hence \(f(x+y)=g(\pi(x+y))\neq n\)
\item If  \(\lambda(y)\neq \lambda(x+y)\), \(\lambda(y)+1= \lambda(x+y)\)\\
\(n=f(y)=n-1+h(\lambda(y))\). Hence \(h(\lambda(y))=1\).
\\Moreover \(h(1)=1\), therefore \(h(\lambda(y)+1) \neq 1\)
\\if \(\pi(x+y) \in A_n\), \(f(x+y)=n-1+h(\lambda(x+y))>n\)
\end{itemize}

\underline{if \((x,y) \in (\mathcal{C})^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases:

\begin{itemize}
\item If \(\pi(x)+\pi(y)>q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) (qv previous proposition)
\\Hence \(g(\pi(x+y))= g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))\)
\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
\item If  \(\pi(x)+\pi(y)\leqslant q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) since \(g\) is sum-free for \(x>b\)
\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
\\else, \(f(x+y)=g(\pi(x+y))=g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))=f(x)\)

@@

\underline{if \((x,y) \in \mathcal{C} \times \mathcal{R} \), \(f(x)\neq f(y)\)}\\

\underline{if \((x,y) \in (\mathcal{R})^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
\\Let \(r(x)=\pi(x)-a\) and \(r(y)=\pi(y)-a\),
\\We proved that \(x=a\lambda(x)+\pi(x)-a\), therefore \(x=a\lambda(x)+\pi(x)\)
\\\(x+y=a(\lambda(x)+\lambda(y))+r(x)+r(y)\). We distinguish three cases:

@@

\item If \(r(x)+r(y)>b\), \(\pi(x)+\pi(y)>2a+b\)
\\Since \(g\) is a \(b\)-WSF template, \(g(\pi(\pi(x)+\pi(y))) \neq n\)
\\Therefore, \(g(\pi(x+y)) \neq n\) ie \(x+y \in \mathcal{C}\)
\\Hence \(f(x+y) <n\leqslant f(x)\)
\item If \(r(x)+r(y) \leqslant b - a\), \(\pi(x)+\pi(y)\leqslant b+a\)
\\Since \(g\) is sum-free for \(x>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
\\Hence, \(f(x+y) <n\leqslant f(x)\)
\end{itemize}
